DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-05-26 2015CompleteDerivation/completeDerivation.tex
Paragraph on functions didn't get checked in

\title{DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi}
\affiliation{University of Michigan, Ann Arbor, MI 48109}
\email{carcassi@umich.edu}
\date{\today}

@@

>>>>

\title{DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi, Christine A. Aidala, David J. Baker, Lydia Bieri}
\affiliation{University of Michigan, Ann Arbor, MI 48109}
\email{carcassi@umich.edu}
\date{\today}

@@

As we identified the set of Lebesque integrable continuous functions $C(\mathcal{S}) \cap  L^1(\mathcal{S}, \mu)$ as the set of distributions that are physically meaningful, we can better understand why other commonly used function spaces do not fit the bill. Some are not restrictive enough. The set of Lebesgue integrable functions $L^1(\mathcal{S})$ includes discontinuous functions that for \ref{continuous_map} are unphysical. The set of continuous functions $C(\mathcal{S})$ and the set of continuous functions that vanish at infinity $C_0(\mathcal{S})$ include functions whose integral is infinite, which would represent infinite amount of material. Some are too restrictive. The set of continuous functions with compact support $C_C(\mathcal{S})$ would exclude distributions, such as Gaussians, that span over the whole range of states. If we take a finite volume of an ideal gas at equilibrium, the momentum distribution spans over the whole range. Schwartz space $S(\mathcal{S})$ excludes functions that are not infinitely smooth which we don't have a general physical justification for.
